Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2020-11-03 theory.tex
Adding information about ideal stage from ideal cut algorithm

As illustrated in Fig. \ref{fig_a_m_b}, $\theta$ ensures an ideal feeding
stage to the cascade ranges between 0.45 and 0.525, depending on the feed assay.

>>>>

To construct an ideal cascade stage, a stage cut ($\theta$) must first be computed.
This is found iteratively, searching for the optimal cut value where $\alpha = \beta$
for a given feed and centrifuge parameters. With a separative power calculated,
and $\alpha$ and $\beta$ value can be determined for an initial cut guess. This
model assumes that the ideal cut for a stage should be between 0.1 and 0.9. The
two enrichment factors are compared, and the higher or lower cut value is chosen
by which pair of factors are closer. A new cut is determined from the chosen
factors, a new separative power is computed, and new $\alpha$ and $\beta$ values
are compared. This process continues until, to some precision, the resulting
enrichment factors are approximately equal. As illustrated in Fig. \ref{fig_a_m_b},
for a given input feed assay, the ideal feeding stage typically has a $\theta$
value between 0.45 and 0.525 when $\alpha = \beta$.
